Temporal Dynamics of Normalization Reweighting

### 2023-07-31 manuscript.Rmd
Added code to download the processed intermodulation data if required

if (processdata>0){
load('temp/PilotIM.RData')

@@

if (processdata>0){
load('temp/EEGIM.RData')

@@

if (processdata>0){
load('temp/MEGIM.RData')

>>>>

   if (!file.exists('temp/PilotIM.RData')){
      hid <- pmatch('PilotIM.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }
load('temp/PilotIM.RData')

@@

     if (!file.exists('temp/EEGIM.RData')){
      hid <- pmatch('EEGIM.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }
load('temp/EEGIM.RData')

@@

       if (!file.exists('temp/MEGIM.RData')){
      hid <- pmatch('MEGIM.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }
load('temp/MEGIM.RData')
